Homework 7

### 2019-10-31 hw7/MSimonsHW7.tex
hw 7 problem 1
Cleaned up hw7 and updated pdf for hw5:

\item TODO

@@

\item
\begin{enumerate}
\item
Since $-1 + 3i$ is a root of $f(x)$, $-1 - 3i$ is a root of $f(x)$.
Therefore
\[
f(x) = (x + 1 + 3i)(x + 1 - 3i)(h(x)) = (x^2 + 2x + 10)(h(x))
\] for
some polynomial $h(x)$.
By division,
\[h(x) = f(x) / (x^2 + 2x + 10) = x^4 + x^2 - 6
\]
Thus,
\[f(x) = (x^2 + 2x + 10)(x^4 + x^2 - 6) = (x^2 + 2x + 10)(x^2 + 3)(x^2 - 2)
\]
We know that $(x^2 + 2x + 10)$ and $(x^2 - 2)$ are irreducible in $\mathbb{Q}[x]$
by Eisenstein's Criterion for prime $p = 2$, and $(x^2 + 3)$ is irreducible
in $\mathbb{Q}[x]$ for prime $p = 3$.  Therefore, the irreducible
factorization of $f(x)$ in $\mathbb{Q}[x]$ is
\[
f(c) = (x^2 + 2x + 10)(x^2 + 3)(x^2 - 2)
\]

>>>>

\item If $f(x) = x^7 - 7x + 20$, then
\[
f(x+1) = x^7 + 7x^6 + 21x^5 + 35x^4 + 35x^3 + 21x^2 + 14
\]
By Eisenstein's Criterion, $f(x + 1)$ is irreducible in $\mathbb{Q}[x]$ for $p = 7$,
and so $f(x)$ is irreducible in $\mathbb{Q}[x]$.

@@

\item
\begin{enumerate}
\item
Since $-1 + 3i$ is a root of $f(x)$, $-1 - 3i$ is also a root of $f(x)$.
Therefore
\[
f(x) = (x + 1 + 3i)(x + 1 - 3i)(h(x)) = (x^2 + 2x + 10)(h(x))
\] for
some polynomial $h(x)$.
\\ \\
By division,
\[h(x) = f(x) / (x^2 + 2x + 10) = x^4 + x^2 - 6
\]
Thus,
\[f(x) = (x^2 + 2x + 10)(x^4 + x^2 - 6) = (x^2 + 2x + 10)(x^2 + 3)(x^2 - 2)
\]
We know that $(x^2 + 2x + 10)$ and $(x^2 - 2)$ are irreducible in $\mathbb{Q}[x]$
by Eisenstein's Criterion for prime $p = 2$, and $(x^2 + 3)$ is irreducible
in $\mathbb{Q}[x]$ by Eisenstein's Criterion for prime $p = 3$.
Therefore, the irreducible
factorization of $f(x)$ in $\mathbb{Q}[x]$ is
\[
f(c) = (x^2 + 2x + 10)(x^2 + 3)(x^2 - 2)
\]
